Finite Property Convex Elicitation Notes

### 2018-04-29 cvx-fin-notes.tex
Jessie addedquestions for clarification

A property is \emph{finite} if $\R$ is finite.
A finite property is \emph{ordered} if there is an ordering $\R = \{r_1,\ldots,r_k\}$ such that the intersection of consecutive level sets forms a hyperplane.
\raf{Still not sure what the right definition is for non-finite $\R$... and it would be nice to have a more natural version for finite $\R$!}
In other words, for all $i \in \{1,\ldots,k-1\}$ there is some $a_i\in\reals^n$ such that $\Gamma_{r_i}\cap\Gamma_{r_{i+1}} = \{p\in\P : a_i\cdot p = 0\}$.

@@

\raf{TODO: finish proof that $L'$ elicits $\Gamma'$.  $\Gamma' \supseteq \Gamma \cap \R'$ is easy.}
  Finally, let $L' = L|_{\R'}$.
  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot L(r)$ $ \argmin_{r\in\R'} p\cdot L'(r') $
\end{proof}
Note that non-degeneracy is necessary to make Lemma~\ref{lem:trim} interesting, as otherwise $\Gamma' : p \mapsto \emptyset$ would always suffice.

\begin{definition}\label{def:trim}
  We define $\trim(\Gamma)$ to be the unique $\Gamma'$ in Lemma~\ref{lem:trim}, up to relabeling of the reports.
\end{definition}

\begin{definition}
  We say $L:\R'\times\Y\to\reals$ \emph{essentially elicits} a property $\Gamma : \P \toto \R$ if there exists some injective embdedding $\varphi:\R\to\R'$ such that for all $p\in\P,r\in\R$ we have $r \in \Gamma(p) \iff \varphi(r) \in \Gamma_L(p)$.
  Such a property is \emph{essentially elicitable} and if $L$ is convex, \emph{essentially convex elicitable}.
\end{definition}
Note that in particular, $L$ essentialy elicits $\trim(\Gamma_L)$.

>>>>

A property is \emph{finite} if $\R$ is finite.
\jessie{If $\R$ is finite or $\Y$?  The set of minimizers will be finite, but don't we want $\R$ to be an interval/convex?}
A finite property is \emph{ordered} if there is an ordering $\R = \{r_1,\ldots,r_k\}$ such that the intersection of consecutive level sets forms a hyperplane.
\raf{Still not sure what the right definition is for non-finite $\R$... and it would be nice to have a more natural version for finite $\R$!}
In other words, for all $i \in \{1,\ldots,k-1\}$ there is some $a_i\in\reals^n$ such that $\Gamma_{r_i}\cap\Gamma_{r_{i+1}} = \{p\in\P : a_i\cdot p = 0\}$.

@@

\raf{TODO: finish proof that $L'$ elicits $\Gamma'$.  $\Gamma' \supseteq \Gamma \cap \R'$ is easy.}
  Finally, let $L' = L|_{\R'}$.
  \jessie{What is this notation?}
  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot~L(r)$ $ \argmin_{r\in\R'} p\cdot~L'(r') $
\end{proof}
Note that non-degeneracy is necessary to make Lemma~\ref{lem:trim} interesting, as otherwise $\Gamma' : p \mapsto \emptyset$ would always suffice.

\begin{definition}\label{def:trim}
  We define $\trim(\Gamma)$ \jessie{What is trim?} to be the unique $\Gamma'$ in Lemma~\ref{lem:trim}, up to relabeling of the reports.
\end{definition}

\begin{definition}
  We say $L:\R'\times\Y\to\reals$ \emph{essentially elicits} a property $\Gamma : \P \toto \R$ if there exists some injective embdedding $\varphi:\R\to\R'$ such that for all $p\in\P,r\in\R$ we have $r \in \Gamma(p) \iff \varphi(r) \in \Gamma_L(p)$.
  Such a property is \emph{essentially elicitable} and if $L$ is convex, \emph{essentially convex elicitable}.
\end{definition}
Note that in particular, $L$ essentially elicits $\trim(\Gamma_L)$.
